### 2017-01-19 paper/intro.tex
pass on intro

%% RQ1 + RQ2
We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  In summary, results indicate that $\sim$21\% of
the test suites take at least 1m to run and $\sim$8\% of the test
suites take at least 5m to run.  Considering all the \numMedLong{}
projects (\percentMedLongRunning{} of
\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.} in the
$>$1m group, the average execution time is \averageMedLongRunning{}.
Results also show that individual tests are typically short-running,
taking often less than half a second to run.  Furthermore, we found
that only in rare cases few test cases monopolize execution cost
associated with each test suite.  Overall, these results suggest that
test suite parallelization has the potential to optimize these test
suites.

\Mar{missing connection. why parallelism?}  From these results we
investigated (2) how frequently the projects we considered use
parallelization to speedup test runs.  Our results indicate that
\percentParallelForLongRunning{} of long-running test suites do use
parallelism to speedup execution.  Given the popularity of this
solution, we further studied: (3) what are the causes of high
execution cost in individual tests (CPU vs. IO) and (4) how uniformly
cost is distributed across tests.  These questions help to assess the
impact of parallelization in test suite execution.  Intuitively,
IO-intensive test suites and test suites with uneven distribution of
cost per test are factors that limit the benefits of parallelization.
Results indicate that \Fix{...}  Finally, we investigated (5) what are
the limitations related to parallelization that could justify adoption
resistance.

\Fix{--------------}

\Mar{what about free services (jenkins)?  how much can you scale
  execution and how expensive would that be?}

To illustrate the importance of parallel test execution, \Jbc{TODO -
Write a paragraph motivating this paper.}

This paper reports an empirical study to evaluate the impact of
parallelization options on test execution speedup \Fix{...}\Jbc{TODO -
Summary of the contributions of this paper} .

>>>>

%% RQ1 + RQ2
We selected \numSubjs{} popular Java projects from \github{}
containing Maven build files~\cite{maven} to assess how prevalent
long-running test suites are.  Section~\ref{sec:eval} details our
methodology to select subjects and to isolate our experiments from
environmental noise.  In summary, results indicate that $\sim$21\% of
the test suites take at least 1m to run and $\sim$8\% of the test
suites take at least 5m to run.  Considering all the \numMedLong{}
projects in the $>$1m group (\percentMedLongRunning{} of
\numSubjs{})\Fix{$\leftarrow$this is not right. check macros.}, the
average execution time is \averageMedLongRunning{}.  Results also show
that individual tests are typically short-running, taking often less
than half a second to run.  Furthermore, we found that only in rare
cases few test cases monopolize execution cost associated with each
test suite.  Overall, these results suggest that test suite
parallelization has the potential to optimize these test suites.

%%RQ3
Given the high execution cost associated with a significant number of
\github{} projects, we decided to investigate practical usage of test
suite parallelization.  It is important to note that modern build
systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
accelerate test execution (see Section~\ref{sec:modes}).  To find how
popular are these features in practice, we first analyzed build files
\emph{statically}.  Considering the +1m group of projects
(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
them use some parallelization option.  Considering those projects that
take more than 5m to run (\numLong{} in total), usage of parallelism
increases to 59\% (19/\numLong{}).  Furthermore, we found that
``forking'' virtual machines was the most prevalent parallel mode used
in practice.  It appeared twice as much as any other mode.  This
result suggests that datarace flakiness~\cite{luo-etal-fse2014} may be
a concern to users as ``forking'' creates different independent
processes (\ie{}, Java VM instances) to speedup test execution.  It
does not exploit thread-level concurrency within each VM, which can be
an important source of
contention~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.
\Mar{why 32-19 did not use parallelization?} \Mar{what about free
  services (jenkins)?  how much can you scale execution and how
  expensive would that be?}

\Fix{...Discuss impact...}

%% \Mar{missing connection. why parallelism?}  From these results we
%% investigated (2) how frequently the projects we considered use
%% parallelization to speedup test runs.  Our results indicate that
%% \percentParallelForLongRunning{} of long-running test suites do use
%% parallelism to speedup execution.  Given the popularity of this
%% solution, we further studied: (3) what are the causes of high
%% execution cost in individual tests (CPU vs. IO) and (4) how uniformly
%% cost is distributed across tests.  These questions help to assess the
%% impact of parallelization in test suite execution.  Intuitively,
%% IO-intensive test suites and test suites with uneven distribution of
%% cost per test are factors that limit the benefits of parallelization.
%% Results indicate that \Fix{...}  Finally, we investigated (5) what are
%% the limitations related to parallelization that could justify adoption
%% resistance.

%% To illustrate the importance of parallel test execution, \Jbc{TODO -
%% Write a paragraph motivating this paper.}

%% This paper reports an empirical study to evaluate the impact of
%% parallelization options on test execution speedup \Fix{...}\Jbc{TODO -
%% Summary of the contributions of this paper} .
